|

### 2020-10-09 paper/article.Rmd
WIP

The *Aedes aegypti* mosquito species is the major vector of several arboviral
diseases worldwide, including dengue, yellow fever, Zika, and chikungunya
[@burt2012chikungunya; @jansen2010dengue; @leta2018global;
@thangamani2016vertical]. Over the past 30 years, arboviral incidence has
increased exponentially, with estimates suggesting that dengue is endemic in
around 100 countries, causing 400 million infections and 22 thousands deaths
each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
for most *A. aegypti*-transmitted diseases [@sridhar2018effect;
@world2017dengue], we have seen a number of recent dengue and Zika outbreaks in
Asia, the Caribbean, South America, and the United States
[@carlson2016ecological; @leta2018global]. Chikungunya virus, which was endemic
only to Africa, has already been reported in every region of the world
[@grandadam2011chikungunya; @kraemer2015global; @mayer2017emergence].

Mosquito control is the primary strategy to prevent *A. aegypti*-borne
infections [@beatty2010best; @eisen2009proactive]. The World Health Organization
recommends the elimination of containers and the use of insecticide to reduce
vector breeding, specially in settings where human-vector contacts are frequent,
such as schools, hospitals, and workplaces [@WHO2012global;
@world2020denguecontrol]. However, cleaning breeding sites and insecticide
spraying are labour-intensive processes, and they are often carried out
inconsistently in developing countries [@paz2015dengue; @siddiqui2016use;
@WHO2012global]. In this regard, improving the performance of those responsible
for vector control is essential to the effectiveness of anti-mosquito programmes
worldwide.

Studies show that financial incentives may increase the productivity of health
care workers [@clemens2014physicians; @muthmainnah2017improving;
@ulrich2005does]. However, systematic reviews indicate the available evidence
has methodological shortcomings, such as selection bias and inadequate
experimental blinding, which limit its generalisability [@bassani2013financial;
@flodgren2011overview; @scott2011effect]. Moreover, it remains unclear which
rewarding schemes have a stronger effect on health care worker performance
[@fainman2020design], or whether they have a sustained effect on patient
outcomes [@jha2012long; @langdown2014use].

In this paper, we explore how financial incentives affect the productivity of
health care personnel involved in *A. aegypti* control and measure how monetary
rewards impact dengue hospitalisations in the long run. We run a randomised
field experiment in the city of Rio Verde, Brazil, which has experienced a peak
in dengue infections in the last years. We hired and trained teams of health
care workers to perform simplified procedures designed to exterminate *A.
aegypti* breeding sites. Our experiment consisted of two treatment arms plus a
control condition. The control group received a fixed compensation for
completing their task, and we offered individual or collective bonuses to those
allocated in the two treatment groups. We then measured the impact of the
compensations schemes on the number of breeding sites discovered, larvae
exterminated, and city-level dengue incidence 30, 60, and 120 days after our
intervention.

We find that monetary rewards increase the number of cleaned breeding sites in
both treatment conditions (individual and team bonuses), and that collective
financial incentives also improve larvae extermination. Our results show that
the control group has a high incidence of houses visited in less than two
minutes apart from each other, which suggests that workers may cheat in the
absence of financial incentives. When we combine both treatments, we also find
that the intervention decreases dengue incidence in 10.3%, but the results are
not robust. In summary, we provide experimental evidence that performance
bonuses enhance public service delivery and that small financial incentives may
improve patient outcomes and reduce hospitalisation costs in *Aedes*-endemic
countries.

@@

The second outcome of interest is dengue incidence in the municipality of Rio
Verde measured 4, 8, 12, and 16 days after the intervention. The Rio Verde
Mayor's Office provided us with its annual health care report, which contains
the dates and personal information of patients who had dengue fever and received
hospital treatment from January to September 2018. We georeferenced the home
addresses of the patients and compared the incidence map with the distribution
of our intervention. We also compare dengue incidence in each of the treatment
statuses with incidence figures in the control group. The unit of analysis is
the census tract in both models. We employ a differences-in-differences
estimator to assess the treatment effects. [@angrist2008mostly].

@@

We find that providing financial incentives to health care worker significantly
increase their field productivity. Both our individual bonus and our collective
bonus treatment groups find more *A. aegypti* breeding sites and exterminate
more mosquito larvae than participants in the control condition, which did not
receive performance compensations. Our results also indicate that the
intervention decreases city-wide levels of dengue incidence, but the
coefficients only reach statistical significance when we combine the two
treatments together and contrast them with the control group. Overall, the
findings suggest that monetary payments are an effective method of improving
health worker performance, yet more research is needed to assess whether higher
labour productivity leads to fewer dengue-related hospitalisations.

>>>>

The *Aedes aegypti* mosquito is the major worldwide vector of several arboviral
diseases, including dengue, yellow fever, Zika, and chikungunya
[@burt2012chikungunya; @jansen2010dengue; @leta2018global;
@thangamani2016vertical]. Over the past 30 years, arboviral incidence has
increased exponentially, with estimates suggesting that dengue is endemic in
around 100 countries and causes 400 million infections and 22 thousands deaths
each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
for most *Aedes*-transmitted diseases [@sridhar2018effect;
@world2017dengue], we have seen a number of dengue and Zika outbreaks in Asia,
the Caribbean, South America, and the United States [@carlson2016ecological;
@leta2018global]. Chikungunya virus, which was endemic only to Africa, has
already been reported in every region of the world [@grandadam2011chikungunya;
@kraemer2015global; @mayer2017emergence].

Mosquito control is the primary strategy to prevent *Aedes*-borne infections
[@beatty2010best; @eisen2009proactive]. The World Health Organization
recommends the elimination of containers and the use of insecticide to reduce
vector breeding, specially in settings where human-vector contacts are
frequent, such as schools, hospitals, and workplaces [@WHO2012global;
@world2020denguecontrol]. However, breeding site cleaning and insecticide
spraying are labour-intensive processes, and they are often carried out
inconsistently in developing countries [@paz2015dengue; @siddiqui2016use;
@WHO2012global]. In this regard, improving the performance of those responsible
for mosquito control is essential to the effectiveness of anti-*Aedes*
programmes.

Research shows that financial incentives may increase the productivity of
health care workers [@clemens2014physicians; @muthmainnah2017improving;
@ulrich2005does]. However, systematic reviews indicate that the available
evidence has serious methodological shortcomings, such as selection bias and
inadequate experimental blinding, what limits the generalisability of current
findings [@bassani2013financial; @flodgren2011overview; @scott2011effect].
Moreover, it remains unclear which rewarding schemes have a stronger effect on
health care worker performance [@fainman2020design], and whether monetary
incentives have a sustained effect on patient outcomes [@jha2012long;
@langdown2014use].

In this paper, we explore how financial incentives affect the productivity of
health care personnel involved in *A. aegypti* control and measure how monetary
rewards impact dengue hospitalisations. We run a randomised field experiment in
the city of Rio Verde, Brazil, which has experienced a peak in dengue
infections in the last years. We hired and trained teams of health care workers
to perform simplified procedures designed to exterminate *A. aegypti* breeding
sites. Our experiment consisted of two treatment arms plus a control condition.
The control group received a fixed compensation for completing their tasks, and
we offered individual or collective bonuses to those allocated in the two
treatment groups. We then measured how the different compensations schemes
affect the number of breeding sites discovered, larvae exterminated, and
city-level dengue incidence.

We find that monetary rewards increase the number of cleaned breeding sites in
both treatment conditions (individual and team bonuses), and that collective
financial incentives also improve larvae extermination. Our results show that
the control group has a high number of houses visited in less than two minutes
apart from each other, which suggests that workers may cheat in the absence of
financial incentives. When we combine both treatments, we also find that the
intervention decreases dengue incidence in 10.3%, but the results are not
robust. In summary, we provide experimental evidence that performance bonuses
enhance public service delivery and that small financial incentives may improve
patient outcomes and reduce hospitalisations in *Aedes*-endemic countries.

@@

The second outcome of interest is dengue incidence in the municipality of Rio
Verde measured 4, 8, 12, and 16 days after the intervention. The Rio Verde
Mayor's Office provided us with its annual health care report, which contains
the dates and personal information of patients who had dengue fever and received
hospital treatment from January to September 2018. We georeferenced the home
addresses of the patients and compared the incidence map with the distribution
of our intervention. We also compare dengue incidence in each of the treatment
statuses with incidence figures in the control group. The unit of analysis is
the census tract in both models. We employ a differences-in-differences
estimator to assess the treatment effects [@angrist2008mostly].

@@

We find that financial incentives significantly increase the field productivity
of health care workers fighting *Aedes aegypti*. Subjects in both the
individual and the collective bonus groups locate more mosquito breeding sites
and exterminate more larvae than participants in the control condition. Our
results also show the intervention decreases city-wide levels of dengue
incidence, but the coefficients only reach statistical significance when we
combine the two treatments together and contrast them with the control group.
Overall, the findings suggest that monetary payments are an effective method of
improving health worker performance, yet more research is needed to assess
whether higher labour productivity leads to fewer dengue-related
hospitalisations.
